An indexed construction of semi-simplicial and semi-cubical types

### 2022-06-24 paper/paper.tex
paper: minor polish
paper: partial spell-check

\begin{table}[H]
  \begin{tabularx}{\linewidth}{p{.2\linewidth}|p{.4\linewidth}|p{.3\linewidth}}
    \toprule
    Value of $\nu$ & 1                              & 2                  \\
    \graymidrule
    Interpretation & Augmented semi-simplical types & Semi-cubical types \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

The fibered representation can be illustrated as:
\begin{equation*}
  \begin{tikzcd}
    X_0 : \U{} & X_1 : \U{} \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \U{} \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
  \end{tikzcd}
\end{equation*}

The indexed representation can be illustrated as:
\begin{align*}
  X_0 & : \U{}                                                                                                      \\
  X_1 & : X_0 \times X_0 \rightarrow \U{}                                                                           \\
  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \U{} \\
  \ldots
\end{align*}

One way to obtain one construction from the other is via the \emph{Grothendieck construction}, although this is not relvant to our work.

\subsection{Iterated parameteriticity}

@@

\begin{enumerate}
  \item[(i)] UIP holds on the unit type.
  \item[(ii)] UIP propogates to $\Sigma$-types.
  \item[(iii)] UIP propogates to $\Pi$-types, with some additional functional extensionality axioms.
\end{enumerate}

@@

\section{Future work}

@@

  \bibitem[Angiuli]{Angiuli17}
  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia), Robert Harper, \& Daniel R. Licata. arXiv preprint.

>>>>

\begin{table}[H]
  \begin{tabularx}{\linewidth}{p{.2\linewidth}|p{.4\linewidth}|p{.3\linewidth}}
    \toprule
    Value of $\nu$ & 1                               & 2                  \\
    \graymidrule
    Interpretation & Augmented semi-simplicial types & Semi-cubical types \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

\subsection{Fibered versus indexed representation}
The fibered representation can be illustrated as:

\begin{equation*}
  \begin{tikzcd}
    X_0 : \U{} & X_1 : \U{} \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \U{} \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
  \end{tikzcd}
\end{equation*}

The indexed representation can be illustrated as:

\begin{align*}
  X_0 & : \U{}                                                                                                      \\
  X_1 & : X_0 \times X_0 \rightarrow \U{}                                                                           \\
  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \U{} \\
  \ldots
\end{align*}

One way to obtain one construction from the other is via the \emph{Grothendieck construction}, although this is not relevant to our work.

\subsection{Iterated parametricity}

@@

\begin{enumerate}
  \item[(i)] UIP holds on the unit type.
  \item[(ii)] UIP propagates to $\Sigma$-types.
  \item[(iii)] UIP propagates to $\Pi$-types, with some additional functional extensionality axioms.
\end{enumerate}

@@

\newpage
\section{Future work}

@@

  \bibitem[Angiuli]{Angiuli17}
  Carlo Angiuli, Guillaume Brunerie, Thierry Coquand, Kuen-Bang Hou (Favonia), Robert Harper, \& Daniel R. Licata. \emph{arXiv preprint}.
